Critical Temperature of the Ising Ferromagnet on Proximity Graphs derived from Square Lattices by Site Displacement

### 2013-11-26 Tex/paper/abstract.tex

Monte Carlo simulations are performed
to determine the critical temperatures of an Ising Ferromagnet on
proximity graphs Relative Neighborhood graph and Gabriel graph which are
subgraphs of the Delaunay Triangulation. The graphs are derived
from square lattices which nodes are displaced by a Gaussian distributed
random variable to the limit of a Poisson point process. The coupling is
set to be depended on the distance of
the nodes. The deviation of the proximity graph from a square lattice is
governed by the width of the Gaussian distribution \(\sigma\). Because
only the lattice structure and coupling is changed, it is expected that
this model lies within the square lattice Ising Ferromagnet universality
class. This expectation is confirmed.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.

>>>>

We perform Monte Carlo simulations to determine the critical temperatures
of an Ising Ferromagnet (IFM) coupled to different types of 2D proximity
graphs.
%~ In particular we consider Relative Neighborhood graphs and Gabriel graphs
%~ which are subgraphs of the Delaunay Triangulation for a given set of points.
The graphs are derived from square lattices where nodes are displaced by
a Gaussian distributed random variable.
%~ The limit of maximal disorder thus corresponds to a Poisson point process.
The deviation of the proximity graph from a square lattice is
governed by the width \(\sigma\) of the Gaussian distribution.
In our model, the coupling strength depends on the euclidian distance
between the coupled spins.
The critical temperatures are shown to depend mainly on the average degree
and the type of the underlying proximity graph.
We further verify that the model lies within the universality class of
the 2D IFM.
